\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

%\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}



\begin{center}
    {\LARGE Ilya Balashov} \\ \vspace{2pt}
    \begin{multicols}{2}
    \begin{flushleft}
    \href{{github.com/ibalashov24}}{GitHub}\\
    \href{{https://www.linkedin.com/in/ibalashov24/}}{LinkedIn}
    \end{flushleft}
    
    \begin{flushright}
%    \href{{your personal websit link}}{my personal site}\\
    \href{mailto:{ilya.v.balashov@gmail.com}}{ilya.v.balashov@gmail.com}\\
    +7 (952) 398-32-88
    
    \end{flushright}
    \end{multicols}
\end{center}


%-----------EDUCATION-----------
\vspace{-2pt}
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Saint Petersburg State University -- Faculty of Math and Mechanics}{Sep. 2017 -- Jul. 2021}
      {BSc, Software and Administration of Information Systems, GPA 4.91/5.00}{Saint Petersburg, Russia}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Research Intern, JetBrains Research}{Oct. 2019 -- Apr. 2021}
      {\href{https://research.jetbrains.org/groups/plt_lab/projects/pe-for-gpgpu/}{Partial evaluation research in Programming Languages and Tools lab}}{Saint Petersburg, Russia}
      \resumeItemListStart
        \resumeItem{Implemented experiments on partial evaluation (C++, CUDA/OpenCL, custom DSLs and LLVM IR)}
        \resumeItem{Developed benchmarks on graph algorithms performance (SuiteSparse GraphBLAS)}
        \resumeItem{Modified Clang slightly for partial evaluation framework support}
        \resumeItem{Finishing bachelor thesis "Partial Evaluation Of Linear Algebra Algorithms" and a paper for SYRCoSE}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------


%-----------CERTIFICATIONS-----------
\section{Projects}
 \resumeSubHeadingListStart
 	\resumeSubheading{TRIK Gamepad Android application modification}{Jun. 2019 -- Aug. 2019}
 	{\href{{https://play.google.com/store/apps/details?id=com.trikset.gamepad}}{Google Play (Beta branch)}
 	}{}
 	\resumeItemListStart
 		\resumeItem{Implemented several new screens and remade networking code}
 		\resumeItem{Covered code with different types of tests}
 		\resumeItem{Connected with Circle CI}
 	\resumeItemListEnd
 	
 	\resumeSubheading{Testing system for TRIK robots programs}{Feb. 2019 -- Jun. 2019}
 	{\href{https://github.com/ibalashov24/semester\_4\_coursework}{Github}}
 	{}
 	\resumeItemListStart
 	\resumeItem{Connected TRIK robot simulator with Travis CI}
 	\resumeItem{Implemented the ability to use simulator as cloud-based testing system}
 	\resumeItemListEnd
 	
 	\resumeSubheading{Google Drive integration plugin for REAL.NET visual programming environment}{Sep. 2018 -- Dec. 2018}
 	{\href{https://github.com/yurii-litvinov/REAL.NET/pull/61/}{Github}}{}
 	\resumeItemListStart
 	\resumeItem{Implemented .Net-based plugin with file managed functionality}
 	\resumeItem{Connected plugin with Google Drive}
 	\resumeItemListEnd
 \resumeSubHeadingListEnd
 
 %-----------PROGRAMMING SKILLS-----------
 \section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
 	\small{\item{
 			\textbf{Programming Languages and Technologies}{: C/C++ , Linux, SQL, Git, CUDA/OpenCL (university courses), Docker, familiarity with Java/Kotlin, Haskell, .NET stack} \\
 			\textbf{Languages}{: Russian (native), English (B2, Upper Intermediate)} 
 	}}
 \end{itemize}

\end{document}